\ab{Constraints on the quasi-normal mode frequencies of the LIGO-Virgo signals by making full use of gravitational-wave modeling}

### 2021-01-17 papers/intro_paper/intro_paper.tex
changes up to Sec. III
updated SXS:BBH:0166 results

\section{Method}

@@

\subsection{Bayesian parameter estimation}\label{sec:method}

@@

\section{Synthetic-signal injection study}\label{sec:results}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
	\includegraphics[width=0.5\textwidth]{figures/nohair_sxs_0166_placeholder.png}	
	\caption{\textcolor{red}{DEMO FIGURE; RUN ONGOING} Posterior probability distribution on the fractional deviations (left panel) and the reconstructed (right panel) frequency and damping time of the $(2,\pm 2)$ (blue curves) and $(3,\pm 3)$ (red curves) \ab{QNM,} respectively, \sout{for a numerical relativity signal corresponding to a BBH merger of} \ab{when a NR signal with parameters} $q=6$,  $M=84 \Mo$ and SNR $=75$ \ab{is injected in Gaussian noise and recovered with the $\pSEOB$ waveform model}. The plus signs mark the GR predictions.}
	\label{fig:nohair_sxs}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\ab{\section{Waveform model and statistical strategy to measure quasi-normal modes}}

@@

\ab{\subsection{Bayesian parameter-estimation technique}}
\label{sec:method}

@@

\ab{\section{Synthetic-signal injection study}}
\label{sec:results}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
	\includegraphics[width=0.5\textwidth]{figures/nohair_sxs_0166.png}	
	\caption{\textcolor{red}{PRELIMINARY} Posterior probability distribution on the fractional deviations (left panel) and the reconstructed (right panel) frequency and damping time of the $(2,\pm 2)$ (blue curves) and $(3,\pm 3)$ (red curves) \ab{QNM,} respectively, \sout{for a numerical relativity signal corresponding to a BBH merger of} \ab{when a NR signal with parameters} $q=6$,  $M=84 \Mo$ and SNR $=75$ \ab{is injected in Gaussian noise and recovered with the $\pSEOB$ waveform model}. The plus signs mark the GR predictions.}
	\label{fig:nohair_sxs}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
